Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

# Create simple probability table - check if prob column exists first
if ("prob" %in% names(prob_df)) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(prob, 3)
    ) |>
    select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
    pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
} else {
  # If prob doesn't exist, look for alternative column names
  prob_col_name <- names(prob_df)[grep("prob|response|emmean", names(prob_df), ignore.case = TRUE)[1]]
  if (!is.na(prob_col_name)) {
    prob_table <- prob_df |>
      mutate(
        Probability = round(.data[[prob_col_name]], 3)
      ) |>
      select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
      pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
  } else {
    # Create empty table if we can't find probability column
    prob_table <- data.frame(
      dr_severity = character(),
      any_treatment = character(),
      No_Lapse = numeric(),
      Lapsed = numeric()
    )
    message("Warning: Could not find probability column in emmeans output")
  }
}

kable(prob_table,
      caption = "Predicted Probability of Vision Impairment by Subgroup",
      col.names = c("DR Severity", "Treatment", "No Lapse", "Lapsed"),
      row.names = FALSE)
```

>>>>

# Create simple probability table - find the right column names
prob_col_candidates <- c("prob", "response", "emmean", "estimate", "predicted", "fitted")
prob_col_name <- NULL
for (candidate in prob_col_candidates) {
  if (candidate %in% names(prob_df)) {
    prob_col_name <- candidate
    break
  }
}

# If we still don't have it, try grep
if (is.null(prob_col_name)) {
  prob_col_idx <- grep("prob|response|emmean|estimate", names(prob_df), ignore.case = TRUE)[1]
  if (!is.na(prob_col_idx)) {
    prob_col_name <- names(prob_df)[prob_col_idx]
  }
}

# Check what factor columns we have
factor_cols <- c("dr_severity", "any_treatment", "ever_lapse_binary")
available_factor_cols <- factor_cols[factor_cols %in% names(prob_df)]

if (!is.null(prob_col_name) && length(available_factor_cols) >= 3) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(.data[[prob_col_name]], 3)
    ) |>
    select(all_of(available_factor_cols), Probability)

  # Try to pivot if we have the lapse column
  if ("ever_lapse_binary" %in% names(prob_table)) {
    prob_table <- prob_table |>
      pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
  }
} else {
  # Create empty table if we can't process
  prob_table <- data.frame(
    Message = "Could not create probability table - missing required columns"
  )
  message("Warning: Missing columns for probability table. Available columns: ", 
          paste(names(prob_df), collapse = ", "))
}

kable(prob_table,
      caption = "Predicted Probability of Vision Impairment by Subgroup",
      row.names = FALSE)
```
